---
title: "scrape jeop"
author: "Andrew Mauro"
date: "May 9, 2017"
output: html_document
---


Purpose: create a function to scrape the Jeopardy Archive (http://j-archive.com/) and obtain a database of jeopardy clue categories, answers, and questions. 

Sources/Info: Starter code was obtained from data.world (https://data.world/mkearney/jeopardy) and updated to scrape matching question and answer values, and in addition obtain clue categories for classification. Regular expression analysis was then performed to group clues into broader categories for the purposes of organization and review.

1. Load Packages and create lookup data frames

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = ls())

#install if needed
#install.packages("qdapRegex")
#install.packages("rvest")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("data.table")

library(rvest)
library(dplyr)
library(tidyr)
library(data.table)
library(qdapRegex)



#create category lookup table
catlookup <- data.frame(round = c(rep("J",6), rep("DJ", 6), "FJ"),
                        category = c(seq(1:6), seq(1:6), "NA"),
                        catlookup = c(seq(1:13))
                        )

#create value lookup table
vallookup <- data.frame(round = c(rep("J",5), rep("DJ", 5), "FJ"),
                        clue_pos = c(seq(1:5), seq(1:5), "NA"),
                        value = c(seq(200,1000, 200), seq(400,2000, 400), "FINAL")
                        )
```


2. Create Functions for scraping jeopardy data

```{r}

#multiple gsub function
mgsub <- function(pattern, replacement, x, ...) {
        if (length(pattern)!=length(replacement)) {
        stop("pattern and replacement do not have the same length.")
                }
        result <- x
        for (i in 1:length(pattern)) {
                result <- gsub(pattern[i], replacement[i], result, ...)
                }
        result
        }


#Jeopardy Function

get_jeopardy <- function(gid) {
  
        get_value <- function(x) {
                value <- x %>%
                        html_nodes("td.clue_value_daily_double") %>%
                        html_text()
                if (!isTRUE(length(value) > 0L)) {
                        value <- x %>%
                                html_nodes("td.clue_value") %>%
                                html_text()
                }
                value
                }
            
        get_answer <- function(x) {
                x %>%
                        html_attr("onmouseover") %>%
                        read_html() %>%
                        html_nodes("em.correct_response") %>%
                        html_text()
                }
            
        get_category <- function(x) {
                x %>%
                        html_attr("onmouseover") %>%
                        read_html() %>%
                        html_nodes("table.clue_header") %>%
                        html_text()
                }
        
        ## send GET request (and store response)
        r <- httr::GET(paste0(
                "http://www.j-archive.com/showgame.php?game_id=", gid))
            
        ## read as HTML
        jeop.html <- r[["content"]] %>%
                rawToChar() %>%
                read_html()
         
        ## parse game title
        title <- jeop.html %>%
                html_nodes("title")%>%
                html_text()
        
            
        ## parse clues
        clue <- jeop.html %>%
                html_nodes("table td.clue_text") %>%
                html_text() %>%
                lapply(paste, collapse = " ") %>%
                unlist(use.names = FALSE)
            
        ## parse answers
        answer <- jeop.html %>%
                html_nodes("table tr td div") %>%
                lapply(get_answer) %>%
                lapply(paste, collapse = " ") %>%
                unlist(use.names = FALSE)
            
        ## obtain categories and values
        #parse clue ids and obtain values
                clue_id <- jeop.html %>%
                        html_nodes("table tr td div") %>%
                        html_attr("onmouseover")
                clue_id <- substr(clue_id, 9,19)
                clue_id <- mgsub(clue_id, pattern = c(",", " ", "'","clue_"), replacement = c("","","",""))
                clue_id <- as.data.frame(clue_id) %>% separate(clue_id,c("round","category","clue_pos"), "_", fill = "right")
                clue_id$order <- seq(1:nrow(clue_id))
                clue_id <- merge(clue_id, catlookup, by = c("round","category"), sort = FALSE)
                clue_id <- merge(clue_id, vallookup, by = c("round","clue_pos"), sort = FALSE)
                clue_id <- arrange(clue_id, order)
                value <- as.character(clue_id[,6])
        #parse categories
                category <- as.data.frame(jeop.html %>%
                        html_nodes("table td.category_name") %>%
                        html_text())
                category$catlookup <- seq(1:nrow(category))
                category <- merge(clue_id, category, by = "catlookup")
                category <- arrange(category, order)
                category <- as.character(category[,7])
        
        ## create data frame
                data.frame(game = rep(title, nrow(clue_id)),
                        category = category,
                        value = value,
                        answer = answer,
                        clue = clue,
                        stringsAsFactors = FALSE
                )
                
                
        }

## Get Jeopardy data or if error return empty data frame
get_jeop <- function(x) {
    dat <- tryCatch(
        get_jeopardy(x),
        error = function(e) return(NULL))
    if (is.null(dat)) {
        dat <- data.frame(
            category = character(),
            value = character(),
            answer = character(),
            clue = character(),
            stringsAsFactors = FALSE)
    }
    dat
}

```

3. Apply function to game ids and save output

```{r}

## Select a subset of questions
j <- lapply(5600:5646, get_jeop)


## collapse list into single data frame
j <- do.call("rbind", j)

## count rows
nrow(j)

## check data
check <- j[sample(seq_len(NROW(j))), ]
check[1:50,]

## Save jeop data into data directory.
write.csv(j, "jeop_test.csv")

```


4. Data Clean

```{r}

#Obtain Gamedates
j$gameDate <- as.Date(rm_between(j$game ,"J! ", "aired "), format = "%Y-%m-%d")
j2 <- j
###CATEGORY CLEANING

#default category is general, replace based on text analysis
cats <- as.data.frame(unique(j2$category))
names(cats) <- "category"
cats$category <- as.character(cats$category)
cats$grouping <- "General"

#History Analysis
#general
cats[grep('HISTORY|CENTURY|DECADE|HISTORIC|WAR|BATTLE|GENERALS|KING|ROYAL|MONARCH|QUEEN|PRINCE|PRINCESS|PATRIOT', cats$category), "grouping"] <- "History"
#us
cats[grep('AMERICAN HISTORY|U.S. HISTORY|U.S.|AMERICAN', cats$category), "grouping"] <- "U.S. History"
#asian
cats[grepl('ASIAN HISTORY', cats$category), "grouping"] <- "Asian History"
#european
cats[grepl('EUROPEAN HISTORY', cats$category), "grouping"] <- "European History"
#Presidents
cats[grepl('PRESIDENT|FOUNDING FATHER|WHITE HOUSE', cats$category), "grouping"] <- "Presidents" 

#Art
cats[grepl('^ART| ART | ART$|MUSEUM|RENAISSANCE', cats$category), "grouping"] <- "Art"

#Literature
cats[grepl('LITERATURE|BOOK|AUTHOR|WRITER|BIOGRAPH|POET|FICTION|BESTSELLER|ENLISH LIT|AMERICAN LIT|FOREIGN LIT|PHILOSOPH', cats$category), "grouping"] <- "Literature"

#Film
cats[grepl('MOVIE|FILM|DIRECTOR|ACTOR|ACTRESS|OSCARS|ACADEMY AWARD', cats$category), "grouping"] <- "Movies"

#Sports
cats[grepl('SPORTS|BASEBALL|FOOTBALL|BASKETBALL|SOCCER|HOCKEY|ATHLETE|NFL|NBA|MLB|NHL|MLS|GOLF|ESPN|TRACK & FIELD|OLYMPIC', cats$category), "grouping"] <- "Sports"

#Music
cats[grepl('MUSIC|SONG|SONGWRITER|COMPOSER|CLASSICAL MUSIC|CLASSICAL|SOUNDTRACK|ROCK STAR|R&B|JAZZ|HIP HOP|RAP |POP |ROCK', cats$category), "grouping"] <- "Music"

#Geography
cats[grepl('GEOGRAPHY|CAPITAL|STATES|COUNTRY|COUNTRIES|AIRPORT|COUNTIES|CITY|CITIES|MAP|GEOGRAPHIC|EUROPE |ASIA |AFRICA|ANTARCTICA |LATIN AMERICA |NORTH AMERICA |FLAG|TRAVEL|THE U.N.|TRANSPORTATION|ISLAND|OCEANIA|LAKE|RIVER|SEA|PARK', cats$category), "grouping"] <- "Geography"

#Country Music
cats[grepl('WOMEN OF COUNTRY|COUNTRY SINGERS|COUNTRY DIVAS|NO. 1 COUNTRY HITS|COUNTRY SINGERS|NO. 1 COUNTRY HITS|COUNTRY SINGER|COUNTRY SINGERS WHO ACT|COUNTRY FEMALE VOCALIST OF THE YEAR GRAMMYS|CLASSIC COUNTRY|UNLIKELY COUNTRY TOP 40 PERFORMERS', cats$category), "grouping"] <- "Music"

#bible
cats[grepl('BIBLE|BIBLICAL|APOSTLE|TESTAMENT|GOSPEL', cats$category), "grouping"] <- "Bible"

#Religion
cats[grepl('RELIGION|RELIGIOUS|ISLAM|MUSLIM|JEW|CATHOLIC|CHRISTIAN|REFORMATION|PROVERB', cats$category), "grouping"] <- "Religion"

#Science and Academics
cats[grepl('SCIENCE|CHEMISTRY|BIOLOGY|PHYSICS|ELEMENTS|PERIODIC TABLE|ANIMAL|COMPUTING|COMPUTERS|PLANET|ASTRONOMY|BODY|OLOGY|ROBOT|DOCTOR|SPACE |MARS|MOON|BIRDS|FISH|AQUATIC|MAMMAL|MEDICAL|MEDICINE', cats$category), "grouping"] <- "Science"

#Year
cats[grepl('^[0-9][0-9][0-9][0-9]$', cats$category),"grouping"] <-"Year"

#Word and Letter Play
cats[grepl('\\"[A-Z]+\\"', cats$category), "grouping"] <- "Word and Letter Play"
cats[grepl('\\"+[A-Z]\\"', cats$category), "grouping"] <- "Word and Letter Play"

#Food and Drink
cats[grepl('COOKING|FOOD|DRINK|COFFEE|WINE|BEER|WHISKEY|SCOTCH|LIQOUR|POTENT POTABLE|GROCERY|FRUIT|VEGETABLE|PROTEIN|PASTA|COOK|CEF|DINING|DISHES|CUISINE', cats$category), "grouping"] <- "Food and Drink"

#TV and Pop Culture
cats[grepl('CELEBRIT|GAMES|TV|TELEVISION|HBO|SHOWTIME|BUSINESS|ETIQUETTE|DIGEST|COLLEGE|COLLEGIATE|GAME|TOYS|COMEDY|JOURNALISM|RADIO|CROSSWORD|BEFORE & AFTER|NEWSPAPERS|CHARACTER|FLOWER|NEWS|TABLOID|SCHOOL|AMERICANA', cats$category), "grouping"] <- "Pop Culture"

#Government and Politics
cats[grepl('GOVERNMENT|POLITIC|ELECTION|CAMPAIGN|MONEY|VEEP|POTUS|SUPREME COURT|JUSTICE|LAW', cats$category), "grouping"] <- "Government and Politics"

#How Many?
(1 - (nrow(cats[cats$grouping == "General",]) / nrow(cats))) * 100

#unclassified analysis
unclassed <- cats[cats$grouping == "General",]
write.csv(unclassed, "unclassed.csv")

#str and write
str(cats)
write.csv(cats, "cats.csv")

#merge and write
val <- nrow(j2)
j2 <- merge(j2, cats, by = "category")
nrow(j2) == val
write.csv(j2, "jeopardy.csv")

```


Conclusion: Cleaned jeopardy csv file can be uploaded to a flash card application website (e.g. https://quizlet.com/) by category for an on the go jeopardy game.